Thesis: draft

### 2021-05-21 draft.tex
Update draft.tex
changed clustering and/or modularity to clustering or modularity

The results of the two real-world networks: (i) the Last.fm on-line social network; and (ii) the PGP trust network, discussed in Chapter \ref{chap4}, Section \ref{realnetwork}, will be shared and discussed. For each real-world network, the results will be compared to results obtained from network models with similar average degree, clustering and/or modularity. We will mainly focus on the formation of echo chambers. We will only study balanced initial conditions and we will introduce a fraction of completely stubborn actors. For both real-world networks, the REC and PR filtering algorithms will be compared.

@@

Results for the PGP trust network are compared to results for network models with similar average degree, clustering and/or modularity. The used network models are, all with $N = 10680$: (i) the Watts-Strogatz model with $\left<k\right> = 4$, $\beta = 0.2$ and $\left<cc\right> = 0.266 \pm 0.003$; (ii) the stochastic block model with 60 communities of size 178, $p_\text{cl} = 0.02$, $p_\text{add} = 0.00005$, $\left<k\right> = 4.06 \pm 0.02$ and $Q = 0.868 \pm 0.002$; (iii) the stochastic Watts-Strogatz block model with 60 communities of size 178, each community has the following Watts-Strogatz parameters: $\left<k\right> = 4$, $\beta = 0.12$; edges are added between communities with probability $p_\text{add} = 0.00007$, $\left<k\right> = 4.74 \pm 0.01$, $\left<cc\right> = 0.263 \pm 0.003$ and $Q = 0.842 \pm 0.002$.\\
\newline
In Fig. \ref{echo_vs_fracRes_real_PGP} the formation of echo chambers versus the fraction of completely stubborn actors (fracRes) is studied for the real-world PGP trust network and for the corresponding network models. This is done for both the PR and REC filtering algorithms. \\
\newline
The PR filtering algorithm (Fig. \ref{pr_real_PGP}) shows a decrease in the formation of echo chambers with an increasing fraction of completely stubborn actors for both the PGP trust network and the corresponding network models. The real-world PGP network has a significantly smaller formation of echo chambers compared to the network model with similar clustering and modularity (SBM-WS). This is most likely due to the heterogeneous degree pattern of the PGP network. \\
The REC filtering algorithm (Fig. \ref{rec_real_PGP}) shows an increase in the formation of echo chambers with an increasing fraction of stubborn actors, followed by a decrease if the fraction of stubborn actors is further increased. This is visible for both the PGP trust network and the network models. Again, the PGP network has a smaller formation of echo chambers than the network model with similar clustering and modularity (SBM-WS), due to its heterogeneous degree distribution. The data points for the SBM and the PGP trust network coincide, which may suggest that the hampering in the formation of echo chambers due to a heterogeneous degree distribution is of a similar size as the hampering due to a lack of clustering.
% compare powerlaw community distribution??

>>>>

The results of the two real-world networks: (i) the Last.fm on-line social network; and (ii) the PGP trust network, discussed in Chapter \ref{chap4}, Section \ref{realnetwork}, will be shared and discussed. For each real-world network, the results will be compared to results obtained from network models with similar average degree, clustering or modularity. We will mainly focus on the formation of echo chambers. We will only study balanced initial conditions and we will introduce a fraction of completely stubborn actors. For both real-world networks, the REC and PR filtering algorithms will be compared.

@@

Results for the PGP trust network are compared to results for network models with similar average degree, clustering or modularity. The used network models are, all with $N = 10680$: (i) the Watts-Strogatz model with $\left<k\right> = 4$, $\beta = 0.2$ and $\left<cc\right> = 0.266 \pm 0.003$; (ii) the stochastic block model with 60 communities of size 178, $p_\text{cl} = 0.02$, $p_\text{add} = 0.00005$, $\left<k\right> = 4.06 \pm 0.02$ and $Q = 0.868 \pm 0.002$; (iii) the stochastic Watts-Strogatz block model with 60 communities of size 178, each community has the following Watts-Strogatz parameters: $\left<k\right> = 4$, $\beta = 0.12$; edges are added between communities with probability $p_\text{add} = 0.00007$, $\left<k\right> = 4.74 \pm 0.01$, $\left<cc\right> = 0.263 \pm 0.003$ and $Q = 0.842 \pm 0.002$.\\
\newline
In Fig. \ref{echo_vs_fracRes_real_PGP} the formation of echo chambers versus the fraction of completely stubborn actors (fracRes) is studied for the real-world PGP trust network and for the corresponding network models. This is done for both the PR and REC filtering algorithms. \\
\newline
The PR filtering algorithm (Fig. \ref{pr_real_PGP}) shows a decrease in the formation of echo chambers with an increasing fraction of completely stubborn actors for both the PGP trust network and the corresponding network models. The real-world PGP network has a significantly smaller formation of echo chambers compared to the network model with similar clustering and modularity (SBM-WS). This is most likely due to the heterogeneous degree pattern of the PGP network. \\
The REC filtering algorithm (Fig. \ref{rec_real_PGP}) shows an increase in the formation of echo chambers with an increasing fraction of stubborn actors, followed by a decrease if the fraction of stubborn actors is further increased. This is visible for both the PGP trust network and the network models. Again, the PGP network has a smaller formation of echo chambers than the network model with similar clustering and modularity (SBM-WS), due to its heterogeneous degree distribution. The data points for the SBM and the PGP trust network coincide, which may suggest that the hampering in the formation of echo chambers due to a heterogeneous degree distribution is of a similar size as the hampering due to a lack of clustering.
% compare powerlaw community distribution??
